Hyperparameter Learning \\ for Conditional Mean Embeddings \\ with Rademacher Complexity Bounds : \\ Supplementary Material

### 2018-04-02 ECML2018/paper/mce_appendix_ecml2018.tex
Link external document properly in appendix

	With \cref{thm:pointwise_uniform_convergence}, we can now show the convergence of various estimators based on the conditional embedding, as long as we can show that their estimator error is upper bounded by a multiple of the conditional embedding error in the \gls{RKHS} norm. As such, we turn to the convergence of the empirical decision probability function \eqref[name= , xr=cake]{eq:empirical_decision_probability} below.

	\begin{theorem}[Uniform Convergence of Empirical Decision Probability Function]
		\label{thm:probability_convergence}
		Assuming that $k(x, \cdot)$ is in the image of $C_{XX}$, the empirical decision probability function $\hat{p}_{c} : \mathcal{X} \to \mathbb{R}$ \eqref[name= , xr=cake]{eq:empirical_decision_probability} converges uniformly to the true decision probability $p_{c} : \mathcal{X} \to [0, 1]$ \eqref[name= , xr=cake]{eq:decision_probability} at a stochastic rate of at least $O_{p}((n \lambda)^{-\frac{1}{2}} + \lambda^{\frac{1}{2}})$ for all $c \in \mathcal{Y} = \mathbb{N}_{m}$.

@@

		The empirical decision probability \eqref[name = , xr=cake]{eq:empirical_decision_probability} for class $c \in \mathbb{N}_{m}$ given an example $x \in \mathcal{X}$ is the empirical conditional embedding with $l = \delta$ conditioned at example $x$ evaluated at label $c$,

@@

	\Cref{thm:empirical_probability_is_embedding} shows that the decision function $\bvec{f}(x)$ \eqref[name = , xr=cake]{eq:empirical_decision_probability_vector} of a \gls{MCE} is no more than the empirical conditional embedding estimated from the data.

@@

		Assuming that $k(x, \cdot)$ is in the image of $C_{XX}$, the empirical decision probability vector function $\hat{\bvec{p}} : \mathcal{X} \to \mathbb{R}^{m}$ \eqref[name = , xr=cake]{eq:empirical_decision_probability_vector} converges uniformly to the true decision probability vector function $\bvec{p} : \mathcal{X} \to [0, 1]^{m}$ in the $\ell_{1}$-norm and $\ell_{2}$-norm, where $\bvec{p}(x) := \{p_{c}(x)\}_{c = 1}^{m}$, at a stochastic rate of at least $O_{p}((n \lambda)^{-\frac{1}{2}} + \lambda^{\frac{1}{2}})$ for all $c \in \mathcal{Y} = \mathbb{N}_{m}$.

@@

	The first approach is straight forward, which involves simply computing the information entropy with the clip normalized probabilities \eqref[name = , xr=cake]{eq:empirical_decision_probability_clip_normalized}, at the query point $x \in \mathcal{X}$,

@@

	Assuming that $\mathbb{P}[Y = y | X = x]$ is never exactly zero for all labels $y \in \mathcal{Y}$ and examples $x \in \mathcal{X}$, then $u_{x}(y)$ is bounded on its discrete domain $\mathbb{N}_{m}$. We can thus write $u_{x} = \sum_{c = 1}^{m} - \log{\mathbb{P}[Y = c | X = x]} \delta(c, \cdot)$ which shows that $u_{x}$ is in the span of the canonical kernel features and is thus in the \gls{RKHS}. Hence, similar to the case with decision probabilities, with $u_{x} \in \mathcal{H}_{\delta}$ and $\bvec{u}_{x} := \{u_{x}(y_{i})\}_{i = 1}^{n}$ we let $g = u_{x}$ in \eqref[name = , xr=cake]{eq:empirical_conditional_expectation} and estimate $h(x)$ by

@@

	where $\hat{\bvec{u}}_{x} := \{\hat{u}_{x}(y_{i})\}_{i = 1}^{n}$. Similar to the case with decision probabilities \eqref[name = , xr=cake]{eq:decision_probability}, the information entropy estimate \eqref[name = ]{eq:empirical_information_entropy} is not guaranteed to be non-negative. However, in practice these negative values are close to zero. Furthermore, negative estimated information entropy implies that the model is very confident about its prediction, and it suffices to simply clip the entropy at zero if strict information entropy is required.

@@

	Suppose a set of training data $\{x_{i}, y_{i}\}_{i = 1}^{n}$ is drawn from $\mathbb{P}_{X Y}$ in an \textit{iid} fashion. We denote the one hot encoded target labels of $\{y_{i}\}_{i = 1}^{n}$ by $\bvec{y}_{i} := \{\mathbb{1}_{c}(y_{i})\}_{c = 1}^{m} \in \{0, 1\}^{m}$ and $\bvec{Y} := \begin{bmatrix} \bvec{y}_{1} & \bvec{y}_{2} & \cdots & \bvec{y}_{n} \end{bmatrix}^{T} \in \{0, 1\}^{n \times m}$. Similarly, let $\bvec{y} \in \{0, 1\}^{m}$ denote the one hot encoded target labels for a generic label $y \in \mathcal{Y}$. Let $k_{\theta} : \mathcal{X} \times \mathcal{X} \to [0, \infty)$ be a family of positive definite kernels indexed by $\theta \in \Theta$. As before, we define the shorthand notation for the gram matrices $K_{\theta} := \{k_{\theta}(x_{i}, x_{j}) : i \in \mathbb{N}_{n}, j \in \mathbb{N}_{n}\}$ and $\bvec{k}_{\theta}(x) := \{k_{\theta}(x_{i}, x) : i \in \mathbb{N}_{n}\}$, and $\lambda$ denotes the regularization parameter of the conditional embedding \eqref[name = , xr=cake]{eq:empirical_conditional_embedding}. The \gls{MCE} has a predictor form $\hat{\bvec{p}}(x) = \bvec{f}_{\theta, \lambda}(x)$ \eqref[name = , xr=cake]{eq:empirical_decision_probability_vector} defined by

>>>>

	With \cref{thm:pointwise_uniform_convergence}, we can now show the convergence of various estimators based on the conditional embedding, as long as we can show that their estimator error is upper bounded by a multiple of the conditional embedding error in the \gls{RKHS} norm. As such, we turn to the convergence of the empirical decision probability function \eqref[name= , xr=mce_ecml2018]{eq:empirical_decision_probability} below.

	\begin{theorem}[Uniform Convergence of Empirical Decision Probability Function]
		\label{thm:probability_convergence}
		Assuming that $k(x, \cdot)$ is in the image of $C_{XX}$, the empirical decision probability function $\hat{p}_{c} : \mathcal{X} \to \mathbb{R}$ \eqref[name= , xr=mce_ecml2018]{eq:empirical_decision_probability} converges uniformly to the true decision probability $p_{c} : \mathcal{X} \to [0, 1]$ \eqref[name= , xr=mce_ecml2018]{eq:decision_probability} at a stochastic rate of at least $O_{p}((n \lambda)^{-\frac{1}{2}} + \lambda^{\frac{1}{2}})$ for all $c \in \mathcal{Y} = \mathbb{N}_{m}$.

@@

		The empirical decision probability \eqref[name = , xr=mce_ecml2018]{eq:empirical_decision_probability} for class $c \in \mathbb{N}_{m}$ given an example $x \in \mathcal{X}$ is the empirical conditional embedding with $l = \delta$ conditioned at example $x$ evaluated at label $c$,

@@

	\Cref{thm:empirical_probability_is_embedding} shows that the decision function $\bvec{f}(x)$ \eqref[name = , xr=mce_ecml2018]{eq:empirical_decision_probability_vector} of a \gls{MCE} is no more than the empirical conditional embedding estimated from the data.

@@

		Assuming that $k(x, \cdot)$ is in the image of $C_{XX}$, the empirical decision probability vector function $\hat{\bvec{p}} : \mathcal{X} \to \mathbb{R}^{m}$ \eqref[name = , xr=mce_ecml2018]{eq:empirical_decision_probability_vector} converges uniformly to the true decision probability vector function $\bvec{p} : \mathcal{X} \to [0, 1]^{m}$ in the $\ell_{1}$-norm and $\ell_{2}$-norm, where $\bvec{p}(x) := \{p_{c}(x)\}_{c = 1}^{m}$, at a stochastic rate of at least $O_{p}((n \lambda)^{-\frac{1}{2}} + \lambda^{\frac{1}{2}})$ for all $c \in \mathcal{Y} = \mathbb{N}_{m}$.

@@

	The first approach is straight forward, which involves simply computing the information entropy with the clip normalized probabilities \eqref[name = , xr=mce_ecml2018]{eq:empirical_decision_probability_clip_normalized}, at the query point $x \in \mathcal{X}$,

@@

	Assuming that $\mathbb{P}[Y = y | X = x]$ is never exactly zero for all labels $y \in \mathcal{Y}$ and examples $x \in \mathcal{X}$, then $u_{x}(y)$ is bounded on its discrete domain $\mathbb{N}_{m}$. We can thus write $u_{x} = \sum_{c = 1}^{m} - \log{\mathbb{P}[Y = c | X = x]} \delta(c, \cdot)$ which shows that $u_{x}$ is in the span of the canonical kernel features and is thus in the \gls{RKHS}. Hence, similar to the case with decision probabilities, with $u_{x} \in \mathcal{H}_{\delta}$ and $\bvec{u}_{x} := \{u_{x}(y_{i})\}_{i = 1}^{n}$ we let $g = u_{x}$ in \eqref[name = , xr=mce_ecml2018]{eq:empirical_conditional_expectation} and estimate $h(x)$ by

@@

	where $\hat{\bvec{u}}_{x} := \{\hat{u}_{x}(y_{i})\}_{i = 1}^{n}$. Similar to the case with decision probabilities \eqref[name = , xr=mce_ecml2018]{eq:decision_probability}, the information entropy estimate \eqref[name = ]{eq:empirical_information_entropy} is not guaranteed to be non-negative. However, in practice these negative values are close to zero. Furthermore, negative estimated information entropy implies that the model is very confident about its prediction, and it suffices to simply clip the entropy at zero if strict information entropy is required.

@@

	Suppose a set of training data $\{x_{i}, y_{i}\}_{i = 1}^{n}$ is drawn from $\mathbb{P}_{X Y}$ in an \textit{iid} fashion. We denote the one hot encoded target labels of $\{y_{i}\}_{i = 1}^{n}$ by $\bvec{y}_{i} := \{\mathbb{1}_{c}(y_{i})\}_{c = 1}^{m} \in \{0, 1\}^{m}$ and $\bvec{Y} := \begin{bmatrix} \bvec{y}_{1} & \bvec{y}_{2} & \cdots & \bvec{y}_{n} \end{bmatrix}^{T} \in \{0, 1\}^{n \times m}$. Similarly, let $\bvec{y} \in \{0, 1\}^{m}$ denote the one hot encoded target labels for a generic label $y \in \mathcal{Y}$. Let $k_{\theta} : \mathcal{X} \times \mathcal{X} \to [0, \infty)$ be a family of positive definite kernels indexed by $\theta \in \Theta$. As before, we define the shorthand notation for the gram matrices $K_{\theta} := \{k_{\theta}(x_{i}, x_{j}) : i \in \mathbb{N}_{n}, j \in \mathbb{N}_{n}\}$ and $\bvec{k}_{\theta}(x) := \{k_{\theta}(x_{i}, x) : i \in \mathbb{N}_{n}\}$, and $\lambda$ denotes the regularization parameter of the conditional embedding \eqref[name = , xr=mce_ecml2018]{eq:empirical_conditional_embedding}. The \gls{MCE} has a predictor form $\hat{\bvec{p}}(x) = \bvec{f}_{\theta, \lambda}(x)$ \eqref[name = , xr=mce_ecml2018]{eq:empirical_decision_probability_vector} defined by
